Data Prep: IUCN and AquaMaps

### 2016-02-12 data_explore/data_prep.Rmd
updating so it will pull counts for all the species in spp_all...

``` {r spp_all with observation counts}
spp_all <- read_csv(file.path(dir_data, 'spp_all.csv'))

@@

x <- occ_search(scientificName = spp_all$sciname[1:100], fields = 'minimal', limit = 5)
y <- sapply(x, function(x) x$meta$count)
z <- data.frame(sciname = names(y), obs = y)

@@

plot(ln_obs ~ ln_occurcells, data = z)

>>>>

``` {r counts_spp_all_observations}
spp_all <- read_csv(file.path(dir_data, 'spp_all.csv'))

@@

system.time({
  x <- occ_search(scientificName = spp_all$sciname, fields = 'minimal', limit = 1)
  ### seems linear - 10 names ~ 2.5 sec, 100 names ~ 25 sec, 1000 names, ~250 sec
  ### so 30000 names ~ 7500 sec or 2 hours
})
y <- sapply(x, function(x) x$meta$count)
z <- data.frame(sciname = names(y), obs = y)

@@

plot(ln_obs ~ ln_occurcells, data = z)
plot(obs ~ occurcells, data = z)
print(summary(lm(obs ~ occurcells, data = z)))

write_csv(z, file.path(dir_anx, 'explore_am_v_iucn/occurrence_df.csv'))
